preference

### 2020-07-27 analyses/BB_abund_GAM.Rmd
Refining GAMs, exploring global hierarchical specification

@@

### FL and BB abundance / diversity
```{r echo=FALSE, include=FALSE}
### Per-transect BB abundance: species-level
bb_abund_sp <- net %>%
  dplyr::select(site, date, bb.sp) %>%
  group_by(site, date, bb.sp) %>% # group by bb.sp*transect (and other variables we want to retain)
  summarize(bb.abund = n()) %>% # get bb.sp*transect abundance
  ungroup %>%
  complete(site, date, bb.sp, fill = list(bb.abund = 0)) %>% # complete implicit absences
  mutate(year = factor(year(date))) %>%
  left_join(site_data) %>%
  mutate(yday = yday(date),
         bb.sp = factor(bb.sp),
         management = factor(management)) %>%
  semi_join(net, by = c("site", "date")) %>%
  group_by(year, bb.sp) %>%
  mutate(bb.total.abund = sum(bb.abund))
```

GAM modeling of abundance per bb species
```{r}
### Call models
bb_abund.2010 <- bam(bb.abund ~ s(bb.sp, bs = "re") + management + slope.est + te(yday, elev.mean, 
                                                            by = bb.sp,
                                                            bs= c("tp", "tp"), 
                                                            k=c(10, 10), m=1),
                        data = filter(bb_abund_sp, year == 2010 & bb.total.abund >= 5),
                        discrete = TRUE,
                        family = "poisson",
                        select = TRUE,
                        method = "fREML") %>% getViz()

check.gamViz(bb_abund.2010)
bb_abund.2010.sum <- summary(bb_abund.2010)
print(plot(bb_abund.2010, allTerms = TRUE), pages = 4)

bb_abund.2011 <- bam(bb.abund ~ s(bb.sp, bs = "re") + management + slope.est + te(yday, elev.mean, 
                                                            by = bb.sp,
                                                            bs= c("tp", "tp"), 
                                                            k=c(10, 10), m=1),
                        data = filter(bb_abund_sp, year == 2011 & bb.total.abund >= 5),
                        discrete = TRUE,
                        family = "poisson",
                        select = TRUE,
                        method = "fREML") %>% getViz()

check.gamViz(bb_abund.2011)
bb_abund.2011.sum <- summary(bb_abund.2011)
print(plot(bb_abund.2011 , allTerms = TRUE), pages = 4)

bb_abund.2012 <- bam(bb.abund ~ s(bb.sp, bs = "re") + management + slope.est + te(yday, elev.mean, 
                                                            by = bb.sp,
                                                            bs= c("tp", "tp"), 
                                                            k=c(10, 10), m=1),
                        data = filter(bb_abund_sp, year == 2012 & bb.total.abund >= 5),
                        discrete = TRUE,
                        family = "poisson",
                        select = TRUE,
                        method = "fREML") %>% getViz()

check.gamViz(bb_abund.2012)
bb_abund.2012.sum <- summary(bb_abund.2012)
print(plot(bb_abund.2012 , allTerms = TRUE), pages = 4)
plot(bb_abund.2012)

```

```{r}
bb_abund.2012.pred <- predict(bb_abund.2012)

ggplot(bb_abund.2012.pred, aes(yday, elev.mean, fit)) +
  geom_raster(aes(fill = exp(fit))) +
  #geom_contour(aes(z = fit), color = "black") +
  geom_point(data = filter(fl_abund, year == 2012), 
             aes(yday, elev.mean, size = fl.abund),
             color = "white", alpha = 0.25) +
  scale_fill_viridis_c()
```

>>>>

### Reprex for Strenge Jacke
```{r}
library(reprex)

library(mgcv)
library(dplyr)
library(ggeffects)

data(iris)

data <- iris %>%
  data.frame()

mod <- gam(Petal.Width ~ Species +
             te(Sepal.Length, Sepal.Width, by = Species),
           data = data)

effects <- ggeffect(mod)
means <- ggemmeans(mod)
pred <- ggpredict(mod)
```

@@

### BB abundance / diversity
```{r echo=FALSE, include=FALSE}
### Per-transect BB abundance: species-level
bb_abund_sp <- net %>%
  dplyr::select(site, date, bb.sp) %>%
  group_by(site, date, bb.sp) %>% # group by bb.sp*transect (and other variables we want to retain)
  summarize(bb.abund = n()) %>% # get bb.sp*transect abundance
  ungroup %>%
  complete(site, date, bb.sp, fill = list(bb.abund = 0)) %>% # complete implicit absences
  semi_join(net, by = c("site", "date")) %>%
  mutate(year = factor(year(date))) %>%
  left_join(site_data) %>%
  mutate(yday = yday(date),
         bb.sp = factor(bb.sp),
         management = factor(management),
         site = factor(site),
         transect = factor(transect)) %>%
  group_by(year, bb.sp) %>%
  mutate(bb.total.abund = sum(bb.abund))
```

GAM modeling of abundance per bb species

I think I need to include site as a random effect because if I don't the pseudoreplication of elevation is pretty extreme, especially in 2012 where I have lots of repeated measures. I am not, for example, measuring floral abundance at 1000 m 20 independent times; I'm measuring it 20 times at the same spot. This does, of  course, create identifiability issues insofar as site and elevation are concurved. But I think I need to accept these problems.

```{r}
### Global model
bb_abund.global <- bam(bb.abund ~
                s(bb.sp, bs = "re") +
                s(year, bs = "re") +
                s(site, bs = "re") +
                te(yday, elev.mean, 
                          by = bb.sp,
                          #id = 0,
                          bs= c("gp", "tp"), 
                          k=c(8, 8), 
                          m=1) +
                te(yday, elev.mean, 
                          by = year,
                          #id = 0,
                          bs= c("gp", "tp"), 
                          k=c(4, 4), 
                          m=2),
              data = filter(bb_abund_sp, bb.total.abund >= 5),
              discrete = TRUE,
              family = "tw",
              select = TRUE,
              method = "fREML") %>% getViz(nsim = 500)

bb_abund.global2 <- gam(bb.abund ~
                s(bb.sp, bs = "re") +
                s(year, bs = "re") +
                s(site, bs = "re") +
                te(yday, elev.mean, 
                          by = bb.sp,
                          #id = 0,
                          bs= c("gp", "tp"), 
                          k=c(6, 6), 
                          m=1) +
                te(yday, elev.mean, 
                          by = year,
                          #id = 0,
                          bs= c("gp", "tp"), 
                          k=c(4, 4), 
                          m=2),
              data = filter(bb_abund_sp, bb.total.abund >= 5 & bb.sp %in% c("bss", "pasc", "prat", "pyre")),
              discrete = FALSE,
              family = ziP(),
              select = TRUE,
              method = "REML") %>% getViz(nsim = 500)

ziptest <- gam(bb.abund ~
                t2(yday, elev.mean, 
                          by = bb.sp,
                          #id = 0,
                          bs= c("gp", "tp"), 
                          k=c(3, 3), 
                          m=1),
              data = filter(bb_abund_sp, bb.total.abund >= 5),
              #discrete = FALSE,
              family = ziP(),
              select = TRUE,
              method = "REML") %>% getViz(nsim = 50)

check.gamViz(bb_abund.global)
check.gamViz(bb_abund.global2)
check.gamViz(ziptest)

bb_abund.global.sum <- summary(bb_abund.global)
bb_abund.global2.sum <- summary(bb_abund.global2)

AIC(bb_abund.global, bb_abund.global2)

print(plot(bb_abund.global, allTerms = TRUE), pages = 3)
print(plot(bb_abund.global2, allTerms = TRUE), pages = 3)

bb_abund.global.ck <- check2D(bb_abund.global, x1 = "yday", x2 = "elev.mean")
bb_abund.global.ck + l_gridCheck2D(gridFun = mean)

### 2010
bb_abund.2010 <- bam(bb.abund ~ 
                       s(bb.sp, bs = "re") + 
                       #bb.sp +
                       #s(transect, bs = "re") +
                       management + 
                       s(site, bs = "re") +
                       # te(yday, elev.mean,
                       #    bs= c("gp", "cr"),
                       #    k=c(10, 10),
                       #    m=2) +
                       te(yday, elev.mean, 
                          by = bb.sp,
                          #id = 0,
                          bs= c("gp", "cr"), 
                          k=c(5, 5), 
                          m=2),
                     data = filter(bb_abund_sp, year == 2010 & bb.total.abund >= 5),
                     discrete = TRUE,
                     family = "tw",
                     select = TRUE,
                     method = "fREML") %>% getViz(nsim = 500)

bb_abund.2010.2 <- gam(bb.abund ~ 
                       s(bb.sp, bs = "re") + 
                       #bb.sp +
                       #s(transect, bs = "re") +
                       management + 
                       s(site, bs = "re") +
                       # te(yday, elev.mean,
                       #    bs= c("gp", "cr"),
                       #    k=c(10, 10),
                       #    m=2) +
                       te(yday, elev.mean, 
                          by = bb.sp,
                          #id = 0,
                          bs= c("gp", "cr"), 
                          k=c(5, 5), 
                          m=2),
                     data = filter(bb_abund_sp, year == 2010 & bb.total.abund >= 5),
                     #discrete = TRUE,
                     family = ziP(),
                     select = TRUE,
                     method = "REML") %>% getViz(nsim = 500)

check.gamViz(bb_abund.2010)
check.gamViz(bb_abund.2010.2)
bb_abund.2010.sum <- summary(bb_abund.2010)
print(plot(bb_abund.2010, allTerms = TRUE), pages = 1)
bb_abund.2010.ck <- check2D(bb_abund.2010, x1 = "yday", x2 = "elev.mean")
bb_abund.2010.ck + l_gridCheck2D(gridFun = mean)

### 2011
bb_abund.2011 <- bam(bb.abund ~ 
                       s(bb.sp, bs = "re") + 
                       #bb.sp +
                       #s(transect, bs = "re") +
                       #management + 
                       s(site, bs = "re") +
                       # te(yday, elev.mean,
                       #    bs= c("gp", "cr"),
                       #    k=c(10, 10),
                       #    m=2) +
                       te(yday, elev.mean, 
                          by = bb.sp,
                          #id = 0,
                          bs= c("gp", "cr"), 
                          k=c(10, 10), 
                          m=1),
                     data = filter(bb_abund_sp, year == 2011 & bb.total.abund >= 5),
                     discrete = TRUE,
                     family = "tw",
                     select = TRUE,
                     method = "fREML") %>% getViz(nsim = 500)

  check.gamViz(bb_abund.2011)
concurvity(bb_abund.2011)
bb_abund.2011.sum <- summary(bb_abund.2011)
print(plot(bb_abund.2011, allTerms = TRUE), pages = 1)
bb_abund.2011.ck <- check2D(bb_abund.2011, x1 = "yday", x2 = "elev.mean")
bb_abund.2011.ck + l_gridCheck2D(gridFun = mean)

### 2012
bb_abund.2012 <- bam(bb.abund ~ 
                       s(bb.sp, bs = "re") + 
                       #bb.sp +
                       #s(transect, bs = "re") +
                       management + 
                       s(site, bs = "re") +
                       # te(yday, elev.mean,
                       #    bs= c("gp", "cr"),
                       #    k=c(10, 10),
                       #    m=2) +
                       te(yday, elev.mean, 
                          by = bb.sp,
                          #id = 0,
                          bs= c("gp", "cr"), 
                          k=c(10, 10), 
                          m=2),
                     data = filter(bb_abund_sp, year == 2012 & bb.total.abund >= 5),
                     discrete = TRUE,
                     family = "tw",
                     select = TRUE,
                     method = "fREML") %>% getViz(nsim = 500)

check.gamViz(bb_abund.2012)
bb_abund.2012.sum <- summary(bb_abund.2012)
print(plot(bb_abund.2012, allTerms = TRUE), pages = 1)
bb_abund.2012.ck <- check2D(bb_abund.2012, x1 = "yday", x2 = "elev.mean")
bb_abund.2012.ck + l_gridCheck2D(gridFun = mean)
```

### Tabulate plots
```{r}
t1 <- ggpredict(bb_abund.2010, terms = c("elev.mean"))
plot(t1)

bss2010 <- plot(sm(bb_abund.2010, 4)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. terrestris/lucorum")), x = NULL, y = NULL)

bss2011 <- plot(sm(bb_abund.2011, 4)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. terrestris/lucorum")), x = NULL, y = NULL)
bss2012 <- plot(sm(bb_abund.2012, 4)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. terrestris/lucorum")), x = NULL, y = NULL)

gers2010 <- plot(sm(bb_abund.2010, 5)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. gerstaeckeri")), x = NULL, y = NULL)
gers2011 <- ggplot() #too rare
gers2012 <- plot(sm(bb_abund.2012, 5)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. gerstaeckeri")), x = NULL, y = NULL)

hort2010 <- plot(sm(bb_abund.2010, 6)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. hortorum")), x = NULL, y = NULL)
hort2011 <- plot(sm(bb_abund.2011, 5)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. hortorum")), x = NULL, y = NULL)
hort2012 <- plot(sm(bb_abund.2012, 6)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. hortorum")), x = NULL, y = NULL)

hypn2010 <- plot(sm(bb_abund.2010, 7)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. hypnorum")), x = NULL, y = NULL)
hypn2011 <- plot(sm(bb_abund.2011, 6)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. hypnorum")), x = NULL, y = NULL)
hypn2012 <- ggplot()  #too rare

jone2010 <- plot(sm(bb_abund.2010, 8)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. jonellus")), x = NULL, y = NULL)
jone2011 <- plot(sm(bb_abund.2011, 7)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. jonellus")), x = NULL, y = NULL)
jone2012 <- plot(sm(bb_abund.2012, 7)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. jonellus")), x = NULL, y = NULL)

lapi2010 <- ggplot() # too rare 
lapi2011 <- plot(sm(bb_abund.2011, 8)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. lapidarius")), x = NULL, y = NULL)
lapi2012 <- plot(sm(bb_abund.2012, 8)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. lapidarius")), x = NULL, y = NULL)

mend2010 <- plot(sm(bb_abund.2010, 9)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. mendax")), x = NULL, y = NULL)
mend2011 <- plot(sm(bb_abund.2011, 9)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. mendax")), x = NULL, y = NULL)
mend2012 <- plot(sm(bb_abund.2012, 9)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. mendax")), x = NULL, y = NULL)

mont2010 <- plot(sm(bb_abund.2010, 10)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. monticola")), x = NULL, y = NULL)
mont2011 <- plot(sm(bb_abund.2011, 10)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. monticola")), x = NULL, y = NULL)
mont2012 <- plot(sm(bb_abund.2012, 10)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. monticola")), x = NULL, y = NULL)

muci2010 <- plot(sm(bb_abund.2010, 11)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. mucidis")), x = NULL, y = NULL)
muci2011 <- plot(sm(bb_abund.2011, 11)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. mucidis")), x = NULL, y = NULL)
muci2012 <- plot(sm(bb_abund.2012, 11)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. mucidis")), x = NULL, y = NULL)

pasc2010 <- plot(sm(bb_abund.2010, 12)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. pascuorum")), x = NULL, y = NULL)
pasc2011 <- plot(sm(bb_abund.2011, 12)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. pascuorum")), x = NULL, y = NULL)
pasc2012 <- plot(sm(bb_abund.2012, 12)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. pascuorum")), x = NULL, y = NULL)

prat2010 <- plot(sm(bb_abund.2010, 13)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. pratorum")), x = NULL, y = NULL)
prat2011 <- plot(sm(bb_abund.2011, 13)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. pratorum")), x = NULL, y = NULL)
prat2012 <- plot(sm(bb_abund.2012, 13)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. pratorum")), x = NULL, y = NULL)

psit2010 <- plot(sm(bb_abund.2010, 14)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. psithyrus")), x = NULL, y = NULL)
psit2011 <- plot(sm(bb_abund.2011, 14)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. psithyrus")), x = NULL, y = NULL)
psit2012 <- plot(sm(bb_abund.2012, 14)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. psithyrus")), x = NULL, y = NULL)

pyre2010 <- plot(sm(bb_abund.2010, 15)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. pyrenaeus")), x = NULL, y = NULL)
pyre2011 <- plot(sm(bb_abund.2011, 15)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. pyrenaeus")), x = NULL, y = NULL)
pyre2012 <- plot(sm(bb_abund.2012, 15)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. pyrenaeus")), x = NULL, y = NULL)

soro2010 <- plot(sm(bb_abund.2010, 16)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. soroensis")), x = NULL, y = NULL)
soro2011 <- plot(sm(bb_abund.2011, 16)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. soroensis")), x = NULL, y = NULL)
soro2012 <- plot(sm(bb_abund.2012, 16)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. soroensis")), x = NULL, y = NULL)

wurf2010 <- plot(sm(bb_abund.2010, 17)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. wurflenii")), x = NULL, y = NULL)
wurf2011 <- plot(sm(bb_abund.2011, 17)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  #l_points() +
  labs(title = expression(italic("B. wurflenii")), x = NULL, y = NULL)
wurf2012 <- plot(sm(bb_abund.2012, 17)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  #l_points() +
  guides(fill = FALSE) +
  labs(title = expression(italic("B. wurflenii")), x = NULL, y = NULL)

pdf("./output/BB_abund_major.pdf", height = 11, width = 8.5)
major_sp <- gridPrint(bss2010, bss2011, bss2012, 
                      pasc2010, pasc2011, pasc2012,
                      prat2010, prat2011, prat2012,
                      psit2010, psit2011, psit2012,
                      soro2010, soro2011, soro2012,
                      wurf2010, wurf2011, wurf2012, ncol = 3)
dev.off()

pdf("./output/BB_abund_highelev.pdf", height = 5.5, width = 8.5)
high_elev_sp <- gridPrint(pyre2010, pyre2011, pyre2012, 
                          mend2010, mend2011, mend2012,
                          mont2010, mont2011, mont2012, ncol = 3)
dev.off()

pdf("./output/BB_abund_minor.pdf", height = 11, width = 8.5)
minor_sp <- gridPrint(gers2010, gers2011, gers2012,
                      hort2010, hort2011, hort2012,
                      hypn2010, hypn2011, hypn2012,
                      jone2010, jone2011, jone2012,
                      lapi2010, lapi2011, lapi2012,
                      muci2010, muci2011, muci2012, ncol = 3)
dev.off()

plot(major_sp)
ggsave(major_sp, "./output/BB_abund_major.pdf")
plot(high_elev_sp)
plot(minor_sp)
```

### Bumble bee diversity
```{r}
bb_rich <- bb_abund_sp %>%
  group_by(site, date, yday, year, elev.mean, management) %>%
  summarize(bb.rich = length(unique(bb.sp)))
```
